quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-10 paper-quollr.tex
Added information regarding why trimesh index should be updated

The \texttt{update\_trimesh\_index()} function re-indexes the node IDs to ensure that edge identifiers are sequentially numbered and consistent with downstream analysis.

@@

\subsection{Identifying and removing low-density hexagons}\label{identifying-and-removing-low-density-hexagons}

>>>>

The \texttt{update\_trimesh\_index()} function re-indexes the node IDs to ensure that edge identifiers are sequentially numbered and consistent with downstream analysis. This sequential ordering of edges is essential because software such as \texttt{langevitour} and \texttt{detourr} rely on one-to-one mapping between edges and their corresponding vertices to visualize the mesh.

@@

\subsubsection{Identifying and removing low-density hexagons}\label{identifying-and-removing-low-density-hexagons}
